### 2017-08-22 thesis/misc/appendix.tex
Added marking_response to the thesis directory temporarily

	\cref{fig:appendix/fm_ob_meta_heatmap_icgc} shows the association of the FM obesity metagene with the gene expression pattern of the FM obesity associated genetic signature in the other \gls{icgc} cancer data sets.
	\cref{fig:appendix/fm_ob_meta_box_scatter_icgc} shows the association of the FM obesity metagene scores with the patient \gls{bmi} and \gls{bmi} status.
	Clearly, the FM metagene was able to capture the overall gene expression patterns, but was not significantly associated with the patient \gls{bmi} or \gls{bmi} status.

@@

	The direction of the obesity metagenes identified from the CR data were examined and corrected for (\cref{fig:crob_meta_direction}).
	Gene probes that were common to all obesity associated genetic signatures were used to examine whether the metagene was in the correct direction, relative to the other obesity metagenes

	\begin{figure}[htpb]
		\centering
		\includegraphics[width=0.32\linewidth,page=3]{appendix/cr_meta_direction_raw}
		\includegraphics[width=0.32\linewidth,page=6]{appendix/cr_meta_direction_raw}\\
		\includegraphics[width=0.32\linewidth,page=9]{appendix/cr_meta_direction_raw}
		\includegraphics[width=0.32\linewidth,page=12]{appendix/cr_meta_direction_raw}
		\includegraphics[width=0.32\linewidth,page=15]{appendix/cr_meta_direction_raw}\\
		\includegraphics[width=0.32\linewidth,page=18]{appendix/cr_meta_direction_raw}
		\includegraphics[width=0.32\linewidth,page=21]{appendix/cr_meta_direction_raw}
		\includegraphics[width=0.32\linewidth,page=24]{appendix/cr_meta_direction_raw}\\
		\caption[Directionality of the obesity metagenes in the CR data]{Heatmaps showing the gene expression of the obesity associated genetic signatures with the obesity metagene in \gls{rma}-normalised CR data set.
		The gene probes that were common to all of the obesity associated genetic signatures were used to determine the direction of the obesity metagenes.
		The scales and axes are the same as the previous heatmaps.
		}
		\label{fig:crob_meta_direction}
	\end{figure}

@@

	As shown in \cref{fig:appendix/cr_icgc_heatmap}, the original obesity metagene from the Creighton \textit{et al.} study was reflective of the sample gene expression levels of the obesity associated genetic signature in all of the other \gls{icgc} cancer data sets.
	However, none of the \gls{icgc} cancer data sets (other than the \gls{blca} data set; \cref{fig:crmetaicgc} in \cref{sec:creighton_obesity_metagene}) showed any significant association of the sample \gls{bmi} or \gls{bmi} status with the Or obesity metagene (\cref{fig:appendix/cr_icgc_box_scatter}).
	The heatmaps, box plots and scatter plots for the other CR obesity metagenes in other \gls{icgc} cancer types are not shown, as many of the plots were very similar to the plots from the \gls{blca} data set.
	The statistics from the results of the box and scatter plots in the other \gls{icgc} cancer types were summarised in \cref{tab:degmetacesc,tab:degmetacoad,tab:degmetakirp,tab:degmetalihc,tab:degmetaread,tab:degmetaskcm,tab:degmetaucec}.

	\begin{figure}[htp!]
		\centering
		\includegraphics[width=0.32\linewidth,page=8]{appendix/crtcga_std}\\
		\vspace{1em}
		\includegraphics[width=0.32\linewidth,page=13]{appendix/crtcga_std}
		\includegraphics[width=0.32\linewidth,page=18]{appendix/crtcga_std}
		\includegraphics[width=0.32\linewidth,page=23]{appendix/crtcga_std}\\
		\vspace{1em}
		\includegraphics[width=0.32\linewidth,page=28]{appendix/crtcga_std}
		\includegraphics[width=0.32\linewidth,page=33]{appendix/crtcga_std}
		\includegraphics[width=0.32\linewidth,page=38]{appendix/crtcga_std}\\
		\caption[Obesity metagene from the \citet{Creighton2012} study and the sample gene expressions in the other \gls{icgc} cancer types]{Heatmaps showing the association of obesity metagene from the \citet{Creighton2012} study with sample gene expression from the other \gls{icgc} data sets.
		Level of expression is represented in the top right histogram, where low and high gene expression were colour-coded with blue and red, respectively.
		Each row of the heatmap represents a gene from the obesity associated genetic signature, and each column of the heatmap represents a sample from the \gls{icgc} data.
		The obesity associated metagene scores of the samples are shown in a separate row at top of the heatmap, and the tree diagram of the heirarchical clustering of the genes is shown to the left of the heatmap. }
		\label{fig:appendix/cr_icgc_heatmap}
	\end{figure}

@@

	\section{Obesity associated genetic signature using sample \gls{bmi} values}
	\label{sec:obesity_associated_genetic_signature_using_sample_bmi_values}

	Since all of these obesity associated genetic signatures were derived based on the discrete values of sample \gls{bmi} staus, a genetic signature was identified using the sample \gls{bmi} value (continuous variable).
	Gene probe expressions were correlated with the sample \gls{bmi} values and was corrected for multiple hypothesis testing with \gls{fdr}.
	There were no significant gene that correlated with the sample \gls{bmi} (p \textless{} 0.05).

	With that said, the top 799 gene probes that correlated the most with the sample \gls{bmi} were examined to see if there was any association.
	The results were similar to the other obesity associated genetic signatures: the continuous \gls{bmi} signature significantly associated with sample \gls{bmi} and \gls{bmi} status in the CR data, but did not show any significance in any of the other cancer data.

@@

		\caption{Significantly enriched \gls{go} pathways in \gls{icgc} cancer data}

@@

To determine whether the results from all of the obesity metagene analyses were not showing any association with patient \gls{bmi} because of the \gls{svd}/transformation matrix approach used, the same approach was used with \gls{er} and \gls{pr} pathway associated genetic signatures from the \citet{Gatza2010a} study.
Firstly, both the \gls{er} and \gls{pr} metagenes were generated in the \gls{rma} normalised CR data set.
The generated metagenes were compared with the gene expressions of the corresponding pathway associated genetic signatures, and the association with the patient \gls{er} and \gls{pr} statuses were also examined.
As shown in \cref{fig:er_cr,fig:pr_cr}, both the \gls{er} and \gls{pr} metagenes in the CR data showed assocation with the gene expression pattern of the pathway, and also showed significant association with the patient \gls{er} and \gls{pr} statuses.

>>>>

	\cref{fig:appendix/fm_ob_meta_heatmap_icgc} shows the association of the FM obesity metagene with the gene expression pattern of the FM obesity-associated genetic signature in the other \gls{icgc} cancer data sets.
	\cref{fig:appendix/fm_ob_meta_box_scatter_icgc} shows the association of the FM obesity metagene scores with the patient \gls{bmi} and \gls{bmi} status.
	Clearly, the FM metagene was able to capture the overall gene expression patterns, but was not significantly associated with the patient \gls{bmi} or \gls{bmi} status.

@@

	The direction of the obesity metagenes identified from the CR data were examined and corrected for (\cref{fig:crob_meta_direction}).
	Gene probes that were common to all obesity-associated genetic signatures were used to examine whether the metagene was in the correct direction, relative to the other obesity metagenes

	\begin{figure}[htpb]
		\centering
		\includegraphics[width=0.32\linewidth,page=3]{appendix/cr_meta_direction_raw}
		\includegraphics[width=0.32\linewidth,page=6]{appendix/cr_meta_direction_raw}\\
		\includegraphics[width=0.32\linewidth,page=9]{appendix/cr_meta_direction_raw}
		\includegraphics[width=0.32\linewidth,page=12]{appendix/cr_meta_direction_raw}
		\includegraphics[width=0.32\linewidth,page=15]{appendix/cr_meta_direction_raw}\\
		\includegraphics[width=0.32\linewidth,page=18]{appendix/cr_meta_direction_raw}
		\includegraphics[width=0.32\linewidth,page=21]{appendix/cr_meta_direction_raw}
		\includegraphics[width=0.32\linewidth,page=24]{appendix/cr_meta_direction_raw}\\
		\caption[Directionality of the obesity metagenes in the CR data]{Heatmaps showing the gene expression of the obesity-associated genetic signatures with the obesity metagene in \gls{rma}-normalised CR data set.
		The gene probes that were common to all of the obesity-associated genetic signatures were used to determine the direction of the obesity metagenes.
		The scales and axes are the same as the previous heatmaps.
		}
		\label{fig:crob_meta_direction}
	\end{figure}

@@

	As shown in \cref{fig:appendix/cr_icgc_heatmap}, the original obesity metagene from the Creighton \textit{et al.} study was reflective of the sample gene expression levels of the obesity-associated genetic signature in all of the other \gls{icgc} cancer data sets.
	However, none of the \gls{icgc} cancer data sets (other than the \gls{blca} data set; \cref{fig:crmetaicgc} in \cref{sec:creighton_obesity_metagene}) showed any significant association of the sample \gls{bmi} or \gls{bmi} status with the Or obesity metagene (\cref{fig:appendix/cr_icgc_box_scatter}).
	The heatmaps, box plots and scatter plots for the other CR obesity metagenes in other \gls{icgc} cancer types are not shown, as many of the plots were very similar to the plots from the \gls{blca} data set.
	The statistics from the results of the box and scatter plots in the other \gls{icgc} cancer types were summarised in \cref{tab:degmetacesc,tab:degmetacoad,tab:degmetakirp,tab:degmetalihc,tab:degmetaread,tab:degmetaskcm,tab:degmetaucec}.

	\begin{figure}[htp!]
		\centering
		\includegraphics[width=0.32\linewidth,page=8]{appendix/crtcga_std}\\
		\vspace{1em}
		\includegraphics[width=0.32\linewidth,page=13]{appendix/crtcga_std}
		\includegraphics[width=0.32\linewidth,page=18]{appendix/crtcga_std}
		\includegraphics[width=0.32\linewidth,page=23]{appendix/crtcga_std}\\
		\vspace{1em}
		\includegraphics[width=0.32\linewidth,page=28]{appendix/crtcga_std}
		\includegraphics[width=0.32\linewidth,page=33]{appendix/crtcga_std}
		\includegraphics[width=0.32\linewidth,page=38]{appendix/crtcga_std}\\
		\caption[Obesity metagene from the \citet{Creighton2012} study and the sample gene expressions in the other \gls{icgc} cancer types]{Heatmaps showing the association of obesity metagene from the \citet{Creighton2012} study with sample gene expression from the other \gls{icgc} data sets.
		Level of expression is represented in the top left histogram, where low and high gene expression were colour-coded with blue and red, respectively.
		Each row of the heatmap represents a gene from the obesity-associated genetic signature, and each column of the heatmap represents a sample from the \gls{icgc} data.
		The obesity-associated metagene scores of the samples are shown in a separate row at top of the heatmap, and the tree diagram of the heirarchical clustering of the genes is shown to the left of the heatmap. }
		\label{fig:appendix/cr_icgc_heatmap}
	\end{figure}

@@

	\section{Obesity-associated genetic signature using sample \gls{bmi} values}
	\label{sec:obesity_associated_genetic_signature_using_sample_bmi_values}

	Since all of these obesity-associated genetic signatures were derived based on the discrete values of sample \gls{bmi} staus, a genetic signature was identified using the sample \gls{bmi} value (continuous variable).
	Gene probe expressions were correlated with the sample \gls{bmi} values and was corrected for multiple hypothesis testing with \gls{fdr}.
	There were no significant gene that correlated with the sample \gls{bmi} (p \textless{} 0.05).

	With that said, the top 799 gene probes that correlated the most with the sample \gls{bmi} were examined to see if there was any association.
	The results were similar to the other obesity-associated genetic signatures: the continuous \gls{bmi} signature significantly associated with sample \gls{bmi} and \gls{bmi} status in the CR data, but did not show any significance in any of the other cancer data.

@@

		\caption[Significantly enriched \gls{go} pathways in \gls{icgc} cancer data]{Significantly enriched \gls{go} pathways in \gls{icgc} cancer data}

@@

To determine whether the results from all of the obesity metagene analyses were not showing any association with patient \gls{bmi} because of the \gls{svd}/transformation matrix approach used, the same approach was used with \gls{er} and \gls{pr} pathway-associated genetic signatures from the \citet{Gatza2010a} study.
Firstly, both the \gls{er} and \gls{pr} metagenes were generated in the \gls{rma} normalised CR data set.
The generated metagenes were compared with the gene expressions of the corresponding pathway-associated genetic signatures, and the association with the patient \gls{er} and \gls{pr} statuses were also examined.
As shown in \cref{fig:er_cr,fig:pr_cr}, both the \gls{er} and \gls{pr} metagenes in the CR data showed assocation with the gene expression pattern of the pathway, and also showed significant association with the patient \gls{er} and \gls{pr} statuses.

### 2017-08-22 thesis/misc/appendix2.tex
tmp commit
Added marking_response to the thesis directory temporarily

	\section{Ranking method for the pathway associated genetic signatures}
	\label{sec:ranking_method_for_the_pathway_associated_genetic_signatures}

	To determine whether it was the best to rank the metagene scores based on the number of samples or rank the scores with the probit method, the two ranking methods were compared in scatter plots with the GT pathway metagenes in \gls{rma} or \gls{mas} normalised GT data.
	Since the results from the \gls{rma} and \gls{mas} normalised GT data were so similar to one another, only the results from the \gls{rma} normalised data are presented (\cref{fig:appendix/rank_scatter}).
	\cref{fig:appendix/rank_scatter} showed that the metagene scores for all of the GT pathway associated genetic signatures were approximately the same in either of the ranking methods used.

@@

	\section{Normalisation method for the pathway associated genetic signature transformation matrices}
	\label{sec:normalisation_method_for_pathway_associated_genetic_signature_transformation_matrices}

	To investigate whether the normalisation methods were important in the creation of the pathway associated genetic signature transformation matrices, and whether the normalisation methods of the data affected the resulting metagenes, transformation matrices were generated in \gls{rma} or \gls{mas} normalised GT data set and then applied to the \gls{rma} or \gls{mas} normalised GT data set.
	The results in \cref{fig:appendix/gt_meta_rma_mas} showed less variability of the metagene scores when the metagenes were derived from the data with the same normalisation method, regardless of the transformation matrix used to produce the metagenes.
	This was most clearly demonstrated by the \gls{bcat}, \gls{er}, \gls{ifna}, \gls{ifny}, p53 and \gls{pr} pathway associated genetic signatures.

@@

	The directionality of the pathway metagenes were determined by comparing the metagene values with the gene expression of the representative gene for the pathway associated genetic signature, as well as the gene expression pattern of the pathway signature (\cref{fig:appendix/gt_pathmeta_rank}).
	Together with the original results presented by \citet{Gatza2010a} (\cref{sec:result_from_gatza2010a_study}), the final directions of the pathway metagenes were decided.

	\begin{figure}[htp!]
		\centering
		\includegraphics[width=0.32\linewidth,page=1]{appendix/gtrmastdrank}
		\includegraphics[width=0.32\linewidth,page=2]{appendix/gtrmastdrank}
		\includegraphics[width=0.32\linewidth,page=3]{appendix/gtrmastdrank}\\
		\includegraphics[width=0.32\linewidth,page=4]{appendix/gtrmastdrank}
		\includegraphics[width=0.32\linewidth,page=5]{appendix/gtrmastdrank}
		\includegraphics[width=0.32\linewidth,page=6]{appendix/gtrmastdrank}\\
		\caption[Directionality of the pathway metagenes in the GT data]{Heatmaps showing the gene expression of the pathway associated genetic signatures, pathway metagenes, and the expression of the representative pathway gene in \gls{rma}-normalised GT data set.
		For each pathway associated genetic signature, the gene expression pattern of the signature was plotted in the heatmap.
		The expression of the representative gene for the pathway signature (see \cref{tab:metagene_direction} in \cref{sub:metagene_direction}) was plotted seaparately as a bar above the pathway metagene scores.
		}
		\label{fig:appendix/gt_pathmeta_rank}
	\end{figure}

@@

	The original result from the \citet{Gatza2010a} study were used to determine the directions of the GT pathway associated genetic signatures in \cref{sec:pathway_associated_genetic_signatures_from_gatza2010a_study} (\cref{fig:gatza_paper_res}).

	\begin{figure}[htpb]
		\centering
		\includegraphics[width=0.7\linewidth]{results2/gatzares1}
		\caption[Original result presented in the \citet{Gatza2010a} study]{Heatmap showing the correlation of all of the GT pathway associated genetic signatures with one another.
		Figure adapted from the \citet{Gatza2010a} study.}
		\label{fig:gatza_paper_res}
	\end{figure}

@@

	The correlation of the pathway associated genetic signatures were plotted as heatmaps for the CR, FM and \gls{nzbc} data sets to confirm that the pathway transformation matrices from the GT data set were generating metagenes that were similar to those in the original \gls{rma} normalised GT data.
	Most importantly, the pathway metagenes generated from the transformation matrices had to cluster in a similar pattern as the pathway metagenes in the GT data set.
	This was to confirm that the directionality of the metagenes were conserved even after the transformation matrices were applied to the data set

@@

	The directionality of the CR obesity associated genetic signatures were determined in the \gls{rma} normalised GT data set to make sure these signatures were in the ``correct'' direction, and therefore able to be compared with the pathway associated genetic signatures appropriately.
	As clearly shown in \cref{fig:appendix/ob_meta_dir_gt}, the Res metagene was flipped as the Res metagene was in the oppsite direction compared with the other obesity metagenes.

	\begin{figure}[htp!]
		\centering
		\includegraphics[width=0.32\linewidth,page=1]{appendix/gtobrma}
		\includegraphics[width=0.32\linewidth,page=2]{appendix/gtobrma}
		\includegraphics[width=0.32\linewidth,page=3]{appendix/gtobrma}\\
		\includegraphics[width=0.32\linewidth,page=4]{appendix/gtobrma}
		\includegraphics[width=0.32\linewidth,page=5]{appendix/gtobrma}
		\includegraphics[width=0.32\linewidth,page=6]{appendix/gtobrma}\\
		\includegraphics[width=0.32\linewidth,page=7]{appendix/gtobrma}
		\includegraphics[width=0.32\linewidth,page=8]{appendix/gtobrma}
		\includegraphics[width=0.32\linewidth,page=9]{appendix/gtobrma}\\
		\caption[Heatmaps of all the obesity and the pathway metagenes in the CR, \gls{nzbc} and FM data]{Heatmaps showing the obesity metagenes from the CR data set with the gene expressions of the obesity associated genetic signatures in the \gls{rma} normalised GT data set.
		High and low correlation were represented as red and blue, respectively, where the colours were matched with the values on the scale shown in the top left histogram.}
		\label{fig:appendix/ob_meta_dir_gt}
	\end{figure}

@@

	Correlation of the pathway and obesity associated genetic signatures were plotted in a heatmap for the GT data in \cref{sec:pathway_associated_metagenes_and_obesity_associated_metagenes}.
	In this section, the correlation of these genetic signatures were plotted as heatmaps for the CR, FM and \gls{nzbc} data sets.
	Though each of the heatmaps show slightly different clustering patterns, the results were similar to that in the GT data set; the CR obesity metagenes clustered together in a single group, and FM metagene did not cluster with any other genetic signatures.

@@

	The \gls{pr}-only linear models for the other obesity associated genetic signatures that were generated in the \gls{nzbc} data were summarised in \cref{tab:lm_pr_only_crol,tab:lm_pr_only_res,tab:lm_pr_only_resol,tab:lm_pr_only_ca,tab:lm_pr_only_caol,tab:lm_pr_only_cares,tab:lm_pr_only_caresol,tab:lm_pr_only_or,tab:lm_pr_only_fm}.
	The \gls{pr} pathway metagene was significant in all of the linear models that predicted the obesity metagenes derived from the CR data set \cref{tab:lm_pr_only_crol,tab:lm_pr_only_res,tab:lm_pr_only_resol,tab:lm_pr_only_ca,tab:lm_pr_only_caol,tab:lm_pr_only_cares,tab:lm_pr_only_caresol,tab:lm_pr_only_or}.
	On the other hand, the sample \gls{bmi}/\gls{bmi} status were significant in the linear model that predicted the FM obesity metagene \cref{tab:lm_pr_only_fm}.

@@

	All of the \gls{r} source code used in this project is publicly available at \url{https://github.com/rikutakei/bmi-cancer-code.git}.
	This thesis was written with \LaTeX{}, and the source code is publicly available at \url{https://github.com/rikutakei/mastersDoc.git}.

>>>>

	\section{Ranking method for the pathway-associated genetic signatures}
	\label{sec:ranking_method_for_the_pathway_associated_genetic_signatures}

	To determine whether it was the best to rank the metagene scores based on the number of samples or rank the scores with the probit method, the two ranking methods were compared in scatter plots with the GT pathway metagenes in \gls{rma} or \gls{mas} normalised GT data.
	Since the results from the \gls{rma} and \gls{mas} normalised GT data were so similar to one another, only the results from the \gls{rma} normalised data are presented (\cref{fig:appendix/rank_scatter}).
	\cref{fig:appendix/rank_scatter} showed that the metagene scores for all of the GT pathway-associated genetic signatures were approximately the same in either of the ranking methods used.

@@

	\section{Normalisation method for the pathway-associated genetic signature transformation matrices}
	\label{sec:normalisation_method_for_pathway_associated_genetic_signature_transformation_matrices}

	To investigate whether the normalisation methods were important in the creation of the pathway-associated genetic signature transformation matrices, and whether the normalisation methods of the data affected the resulting metagenes, transformation matrices were generated in \gls{rma} or \gls{mas} normalised GT data set and then applied to the \gls{rma} or \gls{mas} normalised GT data set.
	The results in \cref{fig:appendix/gt_meta_rma_mas} showed less variability of the metagene scores when the metagenes were derived from the data with the same normalisation method, regardless of the transformation matrix used to produce the metagenes.
	This was most clearly demonstrated by the \gls{bcat}, \gls{er}, \gls{ifna}, \gls{ifny}, p53 and \gls{pr} pathway-associated genetic signatures.

@@

	The directionality of the pathway metagenes were determined by comparing the metagene values with the gene expression of the representative gene for the pathway-associated genetic signature, as well as the gene expression pattern of the pathway signature (\cref{fig:appendix/gt_pathmeta_rank}).
	Together with the original results presented by \citet{Gatza2010a} (\cref{sec:result_from_gatza2010a_study}), the final directions of the pathway metagenes were decided.

	\begin{figure}[htp!]
		\centering
		\includegraphics[width=0.32\linewidth,page=1]{appendix/gtrmastdrank}
		\includegraphics[width=0.32\linewidth,page=2]{appendix/gtrmastdrank}
		\includegraphics[width=0.32\linewidth,page=3]{appendix/gtrmastdrank}\\
		\includegraphics[width=0.32\linewidth,page=4]{appendix/gtrmastdrank}
		\includegraphics[width=0.32\linewidth,page=5]{appendix/gtrmastdrank}
		\includegraphics[width=0.32\linewidth,page=6]{appendix/gtrmastdrank}\\
		\caption[Directionality of the pathway metagenes in the GT data]{Heatmaps showing the gene expression of the pathway-associated genetic signatures, pathway metagenes, and the expression of the representative pathway gene in \gls{rma}-normalised GT data set.
		For each pathway-associated genetic signature, the gene expression pattern of the signature was plotted in the heatmap.
		The expression of the representative gene for the pathway signature (see \cref{tab:metagene_direction} in \cref{sub:metagene_direction}) was plotted seaparately as a bar above the pathway metagene scores.
		}
		\label{fig:appendix/gt_pathmeta_rank}
	\end{figure}

@@

	The original result from the \citet{Gatza2010a} study were used to determine the directions of the GT pathway-associated genetic signatures in \cref{sec:pathway_associated_genetic_signatures_from_gatza2010a_study} (\cref{fig:gatza_paper_res}).

	\begin{figure}[htpb]
		\centering
		\includegraphics[width=0.7\linewidth]{results2/gatzares1}
		\caption[Original result presented in the \citet{Gatza2010a} study]{Heatmap showing the correlation of all of the GT pathway-associated genetic signatures with one another.
		Figure adapted from the \citet{Gatza2010a} study.}
		\label{fig:gatza_paper_res}
	\end{figure}

@@

	The correlation of the pathway-associated genetic signatures were plotted as heatmaps for the CR, FM and \gls{nzbc} data sets to confirm that the pathway transformation matrices from the GT data set were generating metagenes that were similar to those in the original \gls{rma} normalised GT data.
	Most importantly, the pathway metagenes generated from the transformation matrices had to cluster in a similar pattern as the pathway metagenes in the GT data set.
	This was to confirm that the directionality of the metagenes were conserved even after the transformation matrices were applied to the data set

@@

	The directionality of the CR obesity-associated genetic signatures were determined in the \gls{rma} normalised GT data set to make sure these signatures were in the ``correct'' direction, and therefore able to be compared with the pathway-associated genetic signatures appropriately.
	As clearly shown in \cref{fig:appendix/ob_meta_dir_gt}, the Res metagene was flipped as the Res metagene was in the oppsite direction compared with the other obesity metagenes.

	\begin{figure}[htp!]
		\centering
		\includegraphics[width=0.32\linewidth,page=1]{appendix/gtobrma}
		\includegraphics[width=0.32\linewidth,page=2]{appendix/gtobrma}
		\includegraphics[width=0.32\linewidth,page=3]{appendix/gtobrma}\\
		\includegraphics[width=0.32\linewidth,page=4]{appendix/gtobrma}
		\includegraphics[width=0.32\linewidth,page=5]{appendix/gtobrma}
		\includegraphics[width=0.32\linewidth,page=6]{appendix/gtobrma}\\
		\includegraphics[width=0.32\linewidth,page=7]{appendix/gtobrma}
		\includegraphics[width=0.32\linewidth,page=8]{appendix/gtobrma}
		\includegraphics[width=0.32\linewidth,page=9]{appendix/gtobrma}\\
		\caption[Heatmaps of all the obesity and the pathway metagenes in the CR, \gls{nzbc} and FM data]{Heatmaps showing the obesity metagenes from the CR data set with the gene expressions of the obesity-associated genetic signatures in the \gls{rma} normalised GT data set.
		High and low correlation were represented as red and blue, respectively, where the colours were matched with the values on the scale shown in the top left histogram.}
		\label{fig:appendix/ob_meta_dir_gt}
	\end{figure}

@@

	Correlation of the pathway and obesity-associated genetic signatures were plotted in a heatmap for the GT data in \cref{sec:pathway_associated_metagenes_and_obesity_associated_metagenes}.
	In this section, the correlation of these genetic signatures were plotted as heatmaps for the CR, FM and \gls{nzbc} data sets.
	Though each of the heatmaps show slightly different clustering patterns, the results were similar to that in the GT data set; the CR obesity metagenes clustered together in a single group, and FM metagene did not cluster with any other genetic signatures.

@@

	The \gls{pr}-only linear models for the other obesity-associated genetic signatures that were generated in the \gls{nzbc} data were summarised in \cref{tab:lm_pr_only_crol,tab:lm_pr_only_res,tab:lm_pr_only_resol,tab:lm_pr_only_ca,tab:lm_pr_only_caol,tab:lm_pr_only_cares,tab:lm_pr_only_caresol,tab:lm_pr_only_or,tab:lm_pr_only_fm}.
	The \gls{pr} pathway metagene was significant in all of the linear models that predicted the obesity metagenes derived from the CR data set \cref{tab:lm_pr_only_crol,tab:lm_pr_only_res,tab:lm_pr_only_resol,tab:lm_pr_only_ca,tab:lm_pr_only_caol,tab:lm_pr_only_cares,tab:lm_pr_only_caresol,tab:lm_pr_only_or}.
	On the other hand, the sample \gls{bmi}/\gls{bmi} status were significant in the linear model that predicted the FM obesity metagene \cref{tab:lm_pr_only_fm}.

@@

	All of the \gls{r} source code used in this project is publicly available at: \url{https://github.com/rikutakei/bmi-cancer-code.git}.
	This thesis was written with \LaTeX{}, and the source code is publicly available at \url{https://github.com/rikutakei/mastersDoc.git}.

### 2017-08-22 thesis/misc/glossary.tex
Added marking_response to the thesis directory temporarily

\newacronym[description={Endothelial-mesenchymal transition}]{emt}{EMT}{endothelial-mesenchymal transition}

@@

\newacronym[description={Mesenchymal-endothelial transition}]{met}{MET}{mesenchymal-endothelial transition}

>>>>

\newacronym[description={Epithelial-mesenchymal transition}]{emt}{EMT}{epithelial-mesenchymal transition}

@@

\newacronym[description={Mesenchymal-epithelial transition}]{met}{MET}{mesenchymal-epithelial transition}
